---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scdtb

<!-- badges: start -->
<!-- badges: end -->

The goal of 'scdtb' is to provide tools for the analysis of single case design data.

## Installation

To install the development version of 'scdtb' from GitHub, use the [devtools](https://devtools.r-lib.org/) package:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("mightymetrika/scdtb")
```


## Analyze Your Data

Use the scdtb() function to launch a 'shiny' application which implements many of the tools in the 'scdtb' package.

The application has the following functionalities:

* Upload a CSV file to be used as the dataset for modeling.
* View the variables available in the uploaded dataset.
* Enter the roles played by the variables in the dataset.
* Create a raw plot of the data.
* Run a mixed effect model.
* Run a crossed lag correlation analysis.
* Run a non-overlap of all pairs computation.
* Run a randomization test.

```{r, eval=FALSE}
library(scdtb)

# Launch application
scdtb()
```

